\documentclass[12pt]{article}

\usepackage[english, russian]{babel}
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\DeclareGraphicsExtensions{.png}
\graphicspath{{images/}}

\usepackage[left=0.05cm,right=1.4cm, top=1cm,bottom=1cm,bindingoffset=0cm]{geometry}

\usepackage{multirow}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{mathtext}
\usepackage{hhline}
\usepackage{ltablex}

\hypersetup{colorlinks=true,urlcolor=blue}

\newcolumntype{e}{>{\hsize=.9\hsize}X}

\begin{document}
    \pagestyle{empty}

    \begin{center}
        \begin{tabular}{ll}
            \hline
            &\\
            \multicolumn{2}{c}{\textbf{Semen A. Fediukovich}}\\
            &\\
            \hline
            &\\
            \textbf{GPA:} & 3.3 / 4.0   \\
            \textbf{Phone number:} & +995-511-195-385  \\
            \textbf{Email:} & yohimik@gmail.com  \\
            \textbf{Github:} & github.com/yohimik   \\
            \textbf{LinkedIn:} & www.linkedin.com/in/s-fedyukovich   \\
            &\\
            \hline
        \end{tabular}
    \end{center}

    \begin{tabularx}{500pt}{eX}
        \textbf{Education} & \\

        &\\

        Bachelors Degree & \underline{ITMO University, St Petersburg, Russia} \\

        ``Informatics and Computer Engineering''

        2017 --- 2022

        & Graduation thesis ``Web Service Lifecycle Automation''.

        Analyzing current git provider's market and choosing the best one for automated DevOps.

        Deploying a web service based on NodeJs using GitLab CI/CD and Docker Compose.

        Setting up and configuring GitLab Runner on a server using Docker.

        Developing GitLab CI/CD pipelines using modern technologies based on Graph Theory.

        Most of the university works are listed in my GitHub repository TexWorks.

        \\

        &\\

        High School & \underline{Faddeev AG SPSU,  St Petersburg, Russia} \\

        ``Mathematics and cybernetics''

        2015 --- 2017

        & In the learning process was special attention to Mathematical Analysis, Combinatorics, Probability Theory, Complex Numbers, Graph theory, Computational Mathematics, and Common Algorithms.

        Figured out many coding exercises (arbitrary-precision Arithmetic, Graph Algorithms, Combinatorics, Functional integration, and interpolation) using Java and C\# programming languages.

        Calculating Pisano period using Java for big numbers as Mathematician project.

        Taking competition in the team and solo Olympic programming.

        Assembling simple robots and coding firmware using Arduino.

        Developing OpenCV bot for Doom 2 as summer practical work.

        One of the final problems was a C++ compiler written in Java (cout, Variables, Conditionals).

        \\

        &\\

        \textbf{Courses} & \\

        &\\

        INTUIT & \underline{NOU INTUIT, St Petersburg, Russia} \\

        ``Algorithmic fundamentals of raster graphics''

        December 2020 --- 72 hours

        & A short introductory course on basic principles and algorithms used in raster computer graphics that covers a wide range of topics, including the problems of color rendering and image compression.\\

        &\\

        INTUIT & \underline{NOU INTUIT, St Petersburg, Russia} \\

        ``Algorithmic foundations of modern computer graphics''

        December 2020 --- 72 hours

        & A short introductory course on the most common algorithms for 2D and 3D graphics including computational geometry and complexities of algorithms.

        \\

        &\\

        INTUIT & \underline{NOU INTUIT, St Petersburg, Russia} \\

        ``Introduction to data structures, machine states and algorithms''

        May 2020 --- 72 hours

        & A short introductory course on discrete structures such as graphs, state machines, and algorithms.\\

        &\\

        Open Education & \underline{ITMO University, St Petersburg, Russia} \\

        ``Linear electrical circuits''

        May 2019 --- 108 hours

        & During the course, the following topics were studied: static and transient modes in DC and sinusoidal AC circuits;
        three-phase circuits and non-sinusoidal current circuits.

        \\

        &\\

        \textbf{Experience} & \\

        &\\

        Remote Front-end Developer & \underline{Urban Sharing, Tbilisi, Georgia} \\

        July 2021 --- June 2022

        & Development and support of web micro-mobility services working across Europe.
        Developing a web service for a new product from scratch (Next.js, Material UI, React, TypeScript, GraphQL, Docker, Google Cloud Platform).
        Presenting team results to the company.
        Planning sprints and creating tasks for Back-end developers.

        \\

        &\\
        &\\
        &\\
        &\\
        &\\
        &\\
        &\\
        &\\
        &\\
        &\\

        Senior Full-stack Developer & \underline{Fora Soft LLC., St Petersburg, Russia} \\

        August 2020 --- February 2021

        & Leading Washington video project management system development.
        Designing microservices architecture and database scheme.
        Choosing the technology stack and development for most parts of the project.
        Reviewing and helping other developers.

        Developing a multi-threaded service for video render that cuts the video into blocks and renders multiple resolutions parallel on multiple servers from cloud to cloud (without saving a local copy).
        Also, processing other file types (documents, audio, images) to be able to preview them in browsers.

        Deploying the project using GitLab CI/CD and Docker Swarm.
        Integrating Docker Swarm with Amazon CloudWatch Logs and providing analytical data based on logs.

        \\

        & (React, Node.js, TypeScript, Amazon S3, Amazon CloudWatch, Multipart Upload, MongoDB, Material UI, Redis, Fast video rendering, ffmpeg, File processing, RabbitMQ, Next.js, Socket.IO)

        Lectures about databases and message brokers (Neo4j and RabbitMQ).

        \\

        Full-stack Developer & \\

        June 2019 --- August 2020

        & Developing back-end and web admin part of E-learning iOS application, for students who want to earn on tutoring, following tasks from Senior Developer.
        Setting up media server Kurento for video calls and integrating payment system (Node.js, MySQL, Redis, WebRTC, Socket.IO, Next.js, React, Bootstrap).
        Deploying the project using GitHub Actions and Docker Compose.\\

        &\\

        Junior Back-end Developer & \underline{Yumasoft Inc., St Petersburg, Russia} \\

        June 2018 --- June 2019

        & Development and support web POS system for restaurants and delivery services (C\#, ASP.NET, HTTP, REST API, SOAP, MS SQL).
        Fixing small bugs and developing new features.
        Solving Point-in-Polygon problem on a sphere for delivery zones.

        \\

        &\\
        &\\
        &\\
        &\\

        Remote Web Developer & \underline{Freelance, St Petersburg, Russia} \\

        November 2017 --- June 2018

        & Searching for orders and coding website layouts according to design (HTML, CSS, JavaScript).
        Developing HTML parsers on Java.
        Fixing small design issues and filling stores databases in WordPress admin.

        \\

        &\\

        \textbf{Projects} &

        \\

        &\\

        2017 --- 2019 & As a test task developed a multi-threaded archiver (GZiper in my GitHub), that breaks a file into multiple blocks and processes them parallel.

        Also developed other tasks that can be found in my GitHub repository.

        Learning Unity game engine and coding simple games are also listed in my GitHub repository.

        Took part in VK Hackathon in 2018th and 2019th years.
        Both times were close to victory, but we were not able to present projects well.

        \\

        &\\

        2015 --- 2017 & Continue learning Microsoft XNA framework and coding games (Tetris and Snake) at not interesting school lessons (was yearning to coding).

        Working as a freelance developer for the first time and completing orders a couple of orders using Java.

        \\

        &\\

        2013 --- 2015 & Learning BASIC at school and solving simple coding exercises with arrays and loops.

        Continue setting up servers for friends in any games.

        Learning C\# from books and coding simple Windows Forms games (Tic-tac-toe and Clicker).

        Learning Microsoft XNA framework and coding simple game fragments.

        Reading books about computer networks and protocols.

        \\

        &\\

        2011 --- 2013 & Developing simple Pac-Man-like games using GameMaker learning from Google and YouTube videos.

        Setting up Minecraft, Half-Life, and Count-Strike servers at home for the whole class in school.

        Learning Java copying code from videos.

        Learning the basics of Pascal and Delphi (variables, arrays, conditionals).

        \\

        &\\

        \textbf{Skills}& \\

        &\\

        \underline{Common} &

        English level Intermediate or B1, teamwork, perseverance, proactive. \\

        &\\

        \underline{Programming languages} &

        JavaScript, Node.Js, Go, C\#. \\

        & \\

        \underline{Layout} &

        HTML, CSS, SASS, CSSinJS, Latex, Figma. \\

        & \\

        \underline{Storage} &

        MySQL, PostgreSQL, Neo4j, MongoDB, Redis. \\

        &\\

        \underline{Deployment} &

        Docker, GitLab CI/CD, Github Actions, Kubernetes. \\

        &\\

        \underline{Frameworks and libraries} &

        React, Next.js, Material UI, Express, Socket.IO, Sequelize, Mongoose. \\

        &\\

        \underline{Protocols} &

        HTTP, WebSocket, REST, GraphQL, TCP/UDP. \\

        &\\
        \underline{Other} &

        RabbitMQ, GIT, Linux, ffmpeg, clean code, micro services, file processing, code review, Jira, Confluence, Slack.
    \end{tabularx}

\end{document}
